### 2015-02-26 examples/qval.nonp.rmd
updated paper

We examine this issue by simulation. First we define a simple simulation function that simulates
a mixture of 0 and non-zero (normally-distributed) beta values.
```{r}
  # simulate n beta-hat values, nnull under the null with altmean and altsd
  # being the mean and sd of beta under the alternative
  simdata = function(n, nnull, altmean, altsd, betahatsd) {
    null = c(rep(1, nnull), rep(0, n - nnull))
    beta = c(rep(0, nnull), rnorm(n - nnull, altmean, altsd))
    betahat = rnorm(n, beta, betahatsd)
    return(list(null = null, beta = beta, betahat = betahat, betahatsd = betahatsd))
  }
  library(ashr)
  library(qvalue)
  library(locfdr)
  library(mixfdr)
```

>>>>

We examine this issue by simulation. First we define a simple simulation function that simulates
a mixture of 0 and non-zero (normally-distributed) beta values.
```{r}
  # simulate n beta-hat values, nnull under the null with altmean and altsd
  # being the mean and sd of beta under the alternative
  simdata = function(n, nnull, altmean, altsd, betahatsd) {
    null = c(rep(1, nnull), rep(0, n - nnull))
    beta = c(rep(0, nnull), rnorm(n - nnull, altmean, altsd))
    betahat = rnorm(n, beta, betahatsd)
    return(list(null = null, beta = beta, betahat = betahat, betahatsd = betahatsd))
  }
  library(ashr)
  library(qvalue)
  library(locfdr)
  library(mixfdr)
  library(knitr)
```
